Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-01 manuscript.tex

As before, we corrected the originally RV's by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction}. Also in this case the proposed correction almost completely addresses the issue when considering the SN or Normal parameters, with values of $R^2$ larger than 0.99. \xavier{Looking at Fig.~\ref{fig:spot.correction}, we see that the activity correction proposed here is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms. In this case the RV rms of the residuals obtained in the case of the Normal parameters is smaller, however,} \xavier{REDO WITH FINAL PLOT with a difference of 6\,$mm.s^{-1}$, we cannot say that this difference is significant. When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear dependance with the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the faculae.

In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summmurized in Table \ref{table:spot.test}, \umberto{we observe that the $\beta_0$, and $\beta_3$, corresponding respectively to the intercept and to the width of the CCF}, are \umberto{not helpful} to understand the variation measured in RV's. This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}. We see also that the ampltitude parameter, with coefficient $\beta_1$ is only useful to explain the RV variation of the spot in the case of the Normal distribution.}

>>>>

As before, the originally RVs were corrected by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction}. 
In this setting, the proposed correction almost completely addresses the issue \jessi{what issue?} when considering the SN or Normal parameters, with values of $R^2$ larger than 0.99. 
Considering Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms. \jessi{Doesn't the facula setting do better getting down to $\sim$0.13 \ms?}
In this case the RV rms of the residuals obtained in the case of the Normal parameters is smaller, however, \xavier{REDO WITH FINAL PLOT with a difference of 6\,$mm.s^{-1}$, we cannot say that this difference is significant. When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear dependance with the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the faculae.

In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summarized in Table \ref{table:spot.test}, \umberto{we observe that the $\beta_0$, and $\beta_3$, corresponding respectively to the intercept and to the width of the CCF}, are \umberto{not helpful} to understand the variation measured in RV's. This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}. We see also that the ampltitude parameter, with coefficient $\beta_1$ is only useful to explain the RV variation of the spot in the case of the Normal distribution.}
